# Linear Assignment (Adzuna project)

Check out the pretty RPubs version [here](http://rpubs.com/pgrimm52/gadsdc_linear_assignment), friends!

## Load base dataset
```{r}
setwd("/Users/philipp/Desktop/salary")
base <- read.csv("train.csv")
typeof(base)
str(base)
```

## Split into training and test datasets (2:1 split)
```{r}
random <- sample(nrow(base), nrow(base)*2/3)
base.train <- base[random,]
base.test <- base[-random,]
```

## Pretty visualizations (for example, Salary by Category)
```{r}
library(ggplot2)
ggplot(base, aes(Category, SalaryNormalized)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Create basic linear model (using the train/test sets created above)
```{r}
model.1 <- lm(SalaryNormalized ~ 1, data=base.train)
pred.1 <- predict(model.1, base.test)

model.2 <- lm(SalaryNormalized ~ Category, data=base.train)
pred.2 <- predict(model.2, base.test)

model.3 <- lm(SalaryNormalized ~ ContractType + ContractTime + Category, data=base.train)
pred.3 <- predict(model.3, newdata=base.test)

model.4 <- lm(SalaryNormalized ~ ContractType*ContractTime + Category, data=base.train)
pred.4 <- predict(model.4, newdata=base.test)
```

## Create evaluation metric function (chosen metric: RSME) & calculate metric for above models
```{r}
rmse <- function(a,b){
  sqrt(mean((a-b)^2))
}

rmse(pred.1, base.test[["SalaryNormalized"]])
rmse(pred.2, base.test[["SalaryNormalized"]])
rmse(pred.3, base.test[["SalaryNormalized"]])
rmse(pred.4, base.test[["SalaryNormalized"]])
```

## Create cross-validation tool (could also have used cv.lm in DAAG package) for testing on entire dataset
```{r}
cross_val <- function(data, label_column, model_formula, folds_number){
  fold <- sample(folds_number, nrow(data), replace=TRUE)
  eval <- sapply(1:folds_number, function(i){
    train <- data[fold != i, ]
    test <- data[fold == i, ]
    model <- lm(model_formula, data=train)
    pred <- predict(model, test)
    return( sqrt( 
      mean( 
        ( pred - test[, label_column] ) ^2 
      )
    ))
  })
  return(mean(eval))
}

my.formula <- SalaryNormalized ~ ContractType*ContractTime + Category
cross_val(base, 11, my.formula, 10)
```
## Search job title for keyword like "Manager" (adding new features)
```{r}
manager_rows <- grep("Manager", base[,2])
base$Manager <- 0
base$Manager[manager_rows] <- 1

my.formula <- SalaryNormalized ~ ContractType*ContractTime + Category + Manager
cross_val(base, 11, my.formula, 10)  
```

## Now test against this model against the real test/solution data
```{r}
my.formula <- SalaryNormalized ~ ContractType*ContractTime + Category + Manager
model.final <- lm(my.formula, data=base)

real.test <- read.csv("test.csv")
real.solution <- read.csv("solution.csv")

manager_rows <- grep("Manager", real.test[,2])
real.test$Manager <- 0
real.test$Manager[manager_rows] <- 1

problem_rows <- c(which(real.test$Category == "Part time Jobs"))
real.test$Category[problem_rows] <- "Other/General Jobs"

real.predictions <- predict(model.final, real.test)
rmse(real.predictions, real.solution[["SalaryNormalized"]])
```

## What's left?

A whole lot! I've only scratched the surface of what can be done as part of this project, and I intend to do much more:
  * Exploit location_tree.txt to create new features (or refine existing ones)
  * Use tm to experiment with the free-form text job description (potentially a gold mine)
  * Play with regularized fits (once I understand them better)
  * Vowpal wabbit? wtf?  