K Nearest Neighbor Implementation
===

*Requirements*

Implement a one-nearest-neighbor algorithm as a function in R that takes three arguments:

- A data frame of numeric columns, the training data.
- A vector of labels for the training data.
- A data frame with the same columns as the first data frames, this one the data to predict for.

The function should return a vector of predicted labels for the test data.

```{r}
#import library with iris data
library(ggplot2)
```


```{r}
#create test data set from beginning of iris
test <- iris[sample(1:150, 5),]
train <- iris[sample(1:150,5),]

#get matrix of distances for each value. Will result in matrix of columns that contain the distance against each point

knearestneighbors <- apply(test[,1:4], 1, 
              function(y, ylabels){
                
               ylabels[which.min(
                 apply(train[,1:4], 1, function(x) return(
                
                  sum(
                  (x-y)^2)
                    ))
                )]
               
  },train[,5]
  )


print(knearestneighbors)
```
