K Nearest Neighbor Implementation
===

*Requirements*

Implement a one-nearest-neighbor algorithm as a function in R that takes three arguments:
  
- A data frame of numeric columns, the training data.
- A vector of labels for the training data.
- A data frame with the same columns as the first data frames, this one the data to predict for.

The function should return a vector of predicted labels for the test data.

```{r}
#import library with iris data
library(ggplot2)
```


getDist <- function(){
  print(x)
  d <- abs(iris - x)
  print(d)

}
u <- c(1,2,3,4,5,6,7,8) - c(4,3,2,1)

```{r}
#create test data set from beginning of iris
small <- head(iris)

#get matrix of distances for each value. Will result in matrix of columns that contain the distance against each point
#[1,1] will be row 1's first value against itself
#[4,1] will be observation 1's fourth value against itself
#[5,1] will be observations 1's first value agianst observation 2's first value
#[1,2] will be observation 2's first value against obsevation 1's first value
what <- apply(small[,1:4], 1, function(y) apply(small[,1:4], 1, function(x) print(x-y)))
print(what)
```
Now I'm stuck. I need to compress the data by summing every four rows column wise so that [1,1] is the total distance of 1 from 1; [1,2] is the total distance of 1 from 2; [2,4] is the total distance of 2 from 4. 

Searching the internet I found the by, seq and cut functions that may help me but I am unable to get to work.

```{r}
#try to apply to each column of what a function that sums the colum by 
apply(what, 2, function(c) by(c, c[seq(from=1,to=24,by=4),], sum))

#forget where on the internet I read about this one
colsums(what(v, nrow=4))

#only does all of small vs the first in iris
apply(small[,1:4],1, function(x) x-iris[1,1:4])

#attempting to get indicies where the cut needs to take place
y<- 1:100
seq(from = 1, to = 24, by =4)

start <- seq(0,24,4)
#end <

#try to implement cut but cut creates weird floating cuts
apply (what, 2, function(c) by (c, cut(1:24, 4), sum))
```
